Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-06-19 Thesis/chapter/03-theoretical-background.tex
delete massive AI sources

\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
%
\subsubsection{Particle Swarm Optimization}
%
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
%
\subsubsection{Linear Regression}
%
\iffalse
\clearpage
%
\todo{ETC}\\
 - playing board games (and beating humans). alpha go zero \cite{Silver2017}\\
 - image recognition for medicine\cite{Li2020,Deo2015,Topol2019}, autonomous driving \cite{Fujiyoshi2019}\\
 - simulating molecules \cite{Westermayr2019}\\
 - medicine (early erkennen of krakheiten like cancer) \href{https://med.stanford.edu/radiology/news/2020/smart-toilet.html}{[src]}\\
 - pig operation \href{https://www.science.org/doi/10.1126/scirobotics.abj2908}{[src]}\\
 - haushaltshilfen \\
 - See protocoll\\
 - cyber security\cite{Sarker2021}\\
 - analysis by synthesis openAI iGPT-2 \href{https://openai.com/blog/image-gpt/}{[src]}\\
 - using similar input data to start training instead of random starting weights\\
 - Sundar Pichai (google ceo): impact of ai will be greater than fire and electricity\\
 - TPUs used in google and alpha go \\
 - NN + computational power made a lot of advances possible\\
 - computer learned to see, \\
 - Google's Jeff Dean generalize over thousands of tasks AI\\
 - Thomas Oxley Neurologist TEDx\\
 - catching and throwing stuff \\
 - trivial spam filters, image\\
 - dr alan d thompson\\
 - fly brain 100k neurons \cite{Zheng2018} \href{https://en.wikipedia.org/wiki/List\_of\_animals\_by\_number\_of\_neurons{[wiki]}}\\
 - better if similar task before \href{https://www.cs.ubc.ca/~amuham01/LING530/papers/radford2018improving.pdf}{[src]}\\
 - In concrete terms, these capabilities lie at the heart of modern technologies such as smartphone voice recognition, autopilot in planes, driverless cars, translation software, new marketing techniques, investment fund managing, advances in security and surveillance software, facial recognition and autonomous drones, amongst other wide-ranging uses.\\
 \href{https://onlinelibrary.wiley.com/doi/full/10.1111/1467-923X.12794}{[src]}\cite{Hassan2020}\\
 - weaponry and war \href{https://futureoflife.org/data/documents/research\_priorities.pdf}{[src]}\\
 - "AI (like any powerful new technology) enables both great new benefits\\
 and novel pitfalls to be avoided"\\
 - embodied systems such as robots (futureoflife)\\
 - random thought: build AI (unsupervised) to train a supervised leanrning AI (learning in generations\\
 - AI open letter \cite{Russel2015}\\
 - AI100 \href{https://ai100.stanford.edu/gathering-strength-gathering-storms-one-hundred-year-study-artificial-intelligence-ai100-2021-study}{[src]}, \\
 - it's looking as if AI will become ubiquituous and permeate all facetes of life. Zeichen dafür are the \td{infamous} zitat from google ceo, "ai fire electricity", eimrates building a AI centered city named Neom and the stanford AI100 report \cite{Littman2021}\\
 - datasets can be augumented with GAN created data [\href{https://arxiv.org/abs/1711.04340}{src}]\\
 - facial recognition to prevent theft of toilet paper \cite{Andrews2017}.\\
 - financial: lending and financial planing ie investing (so called robo-advisors)\cite{Littman2021}\href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai}{[src]}\\
 - Discussion: "Of course, applying recommendation to multiple tasks simultaneously raises the challenging question of how best to make tradeoffs among these different objectives."\cite{Littman2021}\\
 - AI effect \href{https://ai100.stanford.edu/2016-report/section-i-what-artificial-intelligence/defining-ai#\_ftnref3}{[src]} \cite{McCorduck1982} (e.g. spam filter or web search) \\
 - history: Norbert Wiener, Alan Turing, John von Neumann, Dartmouth conference 1956, team of Newell, Simon and Shaw. then: fields, then arten of AI \\
 - beautiful review of McCorduck1982\cite{McCorduck1982} was written by Apter in sthe same year\cite{Apter1982}\\
 - idea: when train supersived, also train unsupervised and see if similar results

\todo{Lanuage: }\\
 - language processing\\
 - natural language turn into computer code \\
 - GPT-3 by openAI language model \\
 - writing an article \url{https://www.theguardian.com/commentisfree/2020/sep/08/robot-wrote-this-article-gpt-3}\\
 - google translate \\
 - sophia \url{https://link.springer.com/article/10.1007/s00146-020-01104-w}\\
 - speach recognition\\
 - \href{https://ai100.stanford.edu/2021-report/standing-questions-and-responses/sq2-what-are-most-important-advances-ai#_2021SQ2ref3}{srouces}\\

\todo{autonomous vehicles:}\\
 - self driving cars\\
 - tesla, goolge, General Motors, Ford\\
 - mayflower autonomous shiop uk to US\\

\todo{creative: }\\
 - make headlines for articles, design info graphics\\
 - google picture search\\
 - Brand mark (create logo)\\
 - Hidrelet Diao: simpsons to real world \\
 - VQGAN + CLIP (openAI?)\\
 - Neuraldivergent : AI generated art\\
 - https://openai.com/blog/image-gpt/\\
 - animating photos, deep fakes\\
 - dall-e 2 \cite{Marcus2022}\\
 - this person does not exist, dalle 2 \\
 - GAN\\
 - make video games \cite{Guzdial2016}\\

 discussion: ein nachteil ist, dass bei EMMA im vornhinein festgelegt wurde welche parameter und danach konnte man entweder die parameter nicht aendern oder einen winzigen Bruchteil der Daten verwenden. whereas a human would (not unlike a GAN) extrapolate unusable data into the usable regime per bauchgefühl

noteable mentions: GAN, language processing, self driving cars, image recognition, playing board games (and beating humans). 
See protocoll
Chapters to read from "UNDERSTANDING MACHINE LEARNING from theory to algorithms" 1,5,9,11,12,14,15,16,20,23,25
dall-e 2 \cite{Marcus2022}\\
vNeumann 4 param elephant \cite{Dyson2004}\\
4 param elephant \cite{Mayer2010}\\
"All models are wrong but some are useful" \cite{Box1979}\\
"THE NEED FOR SIMPLE SCIENTIFIC MODELS - PARSIMONY" \cite{Box1979}\\
"Breakthroughs in machine learning are rapidly changing science and society, yet our fundamental understanding of this technology has lagged far behind." \cite{Belkin2018}\\
\fi

>>>>

\subsubsection{different kinds} 
supervised vs unsupervised
classification (discrete) vs regression
%
\subsubsection{Particle Swarm Optimization}
%
\subsubsection{Princlipal Component Analysis}
reinforcement learning could also have been a nice option
%
\subsubsection{Linear Regression}
%
